%% start of file `Resume_Baris_Aydinoglu.tex'.
%% Copyright 2006-2013 Xavier Danaux (xdanaux@gmail.com).
%
% This work may be distributed and/or modified under the
% conditions of the LaTeX Project Public License version 1.3c,
% available at http://www.latex-project.org/lppl/.

\documentclass[11pt,a4paper,sans]{moderncv}
\moderncvstyle{casual}
\moderncvcolor{blue}
\usepackage[utf8]{inputenc}
\usepackage[scale=0.8]{geometry}

% personal data
\name{baris}{aydinoglu}
\title{full stack developer}
\email{baris@aydinoglu.info}
\phone[mobile]{+90~(532)~697~48~77}
\social[linkedin]{barisaydinoglu}
\social[twitter]{barisaydinoglu}
\social[github]{barisaydinoglu}

%----------------------------------------------------------------------------------
%            content
%----------------------------------------------------------------------------------
\begin{document}
%-----       resume       ---------------------------------------------------------

\makecvtitle

\section{About}
\cvline{}{I'm a full stack web developer who loves working with open source technology. I work best at planning the architecture of web applications and their development life cycles. I've over a decade of web development experience.}

\section{Experience}
\cventry{2010--Present}{Software Specialist}{Garanti Bank}{Istanbul}{Turkey}{
\begin{itemize}%
  \item Worked on development of cross-platform highly scalable seamless mobile banking infrastructure based on hybrid architecture.
  \item Made high-level design choices, dictated technical standards including software coding standards, tools and platforms.
  \item Mentored other colleagues.
  \item Designed social media monitoring architecture.
  \item Solved technical, security and performance issues of web sites and applications for all tiers in infrastructure.
  \item Made performance and stress tests collaborating with system, network and other related groups.
  \item Built social media infrastructure for banking using Java and Spring. Developed several applications connected to Facebook, Foursquare, and Twitter.
  \item Designed and developed architecture of integrating social media with digital banking channels.
  \item Worked on personal and corporate Internet banking development using Java, Maven, Spring, JavaScript, jQuery.
  \item Provided solutions for general problems and enhancements. \end{itemize}
}
\cventry{2009--2010}{R\&D Engineer}{Hewlett--Packard}{Istanbul}{Turkey}{\begin{itemize}%
  \item I was a member of a great team that involves people from USA, Brazil, and Turkey.
  \item As a team, researched and developed semantic faceted search \& navigation. The project implemented using various programming languages and technologies: PHP, C\#, Java, Flex, Lucene.NET, SpringGraph.
\end{itemize}}
\cventry{2009}{Internship}{Veripark}{Istanbul}{Turkey}{VeriPark is a leading global provider of multi-channel delivery, financial CRM, and lending solutions for financial institutions and a major Dynamics CRM implementer in Turkey and MEA.\begin{itemize}%
  \item Developed an expense management automation in C\# using Three Layer Architecture.
\end{itemize}}
\cventry{2008}{Internship}{ASELSAN}{Ankara}{Turkey}{ASELSAN is a Turkish corporation that produces tactical military radios and defense electronic systems for the Turkish Armed Forces.\begin{itemize}%
  \item Implemented asynchronous socket server and client with encryption and compression in C\#.
\end{itemize}}
\cventry{2008}{Internship}{Motorola}{Istanbul}{Turkey}{\begin{itemize}%
  \item Developed a monitoring system that creates alerts from errors in flow of real-time log data, in C and Perl.
  \item The monitoring system scaled to all of the GSM logs. It provided a quick and highly cost effective benchmark of the coverage.
\end{itemize}}

\section{Education}
\cventry{2005--2010}{BS, Computer Engineering}{Istanbul Technical Univercity}{Turkey}{}{{\textbf{Concentration: }}{Evolutionary Algorithms, Multi-Objective Genetic Graph-Based Clustering}}  % arguments 3 to 6 can be left empty

\section{Open Source Projects}
\cventry{Committer}{\href{https://github.com/barisaydinoglu/Detectizr}{Detectizr}}{Open source JavaScript library to detect browser}{}{}{A Modernizr extension to detect device, device model, screen size, operating system, and browser details}
\cventry{Committer}{\href{https://github.com/barisaydinoglu/jquery-cssSelector}{jquery-cssSelector}}{Open source jQuery plugin}{}{}{jQuery plugin for retrieving the specific CSS selector of a DOM object in relation to its topmost parent.}
\cventry{Contributor}{\href{https://github.com/OfficeDev/ews-java-api}{EWS JAVA API}}{Open source java client library to access Exchange web services}{}{}{The API works against Office 365 Exchange Online as well as on premises Microsoft Exchange.}
\cventry{Contributor}{\href{https://github.com/nyroDev/nyroModal}{nyroModal}}{Highly customizable modal window plugin for jQuery}{}{}{}
\cventry{Contributor}{\href{https://github.com/madrobby/dom-monster}{dom-monster}}{A cross-platform, cross-browser bookmarklet that will analyze the DOM \& other features of the page you're on, and give you its bill of health}{}{}{}
\cventry{Contributor}{\href{https://github.com/Mottie/Keyboard}{Virtual Keyboard}}{Open source on-screen keyboard widget using jQuery-UI}{}{}{An on-screen virtual keyboard embedded within the browser window which will popup when a specified entry field is focused.}

\section{Skills}
\cvitem{Languages}{Java, Javascript, PHP, HTML 5, C, C++, C\#}
\cvitem{Database}{MySQL, MongoDB, PostgreSQL, MSSQL}
\cvitem{Deploy Platforms}{Tomcat, Websphere, Amazon EC2}
\cvitem{Libraries}{Spring Framework, JUnit, Wicket, AspectJ, jQuery}
\cvitem{Protocols}{HTTP, REST, JSON, SOAP, SMTP}
\cvitem{SCMs}{Git, SVN}
\cvitem{Dev. Environment}{Eclipse, Ant, JRebel, Visual Studio}

\section{Interests}
\cvdoubleitem{}{Travelling}{}{Watching Movies}
\cvdoubleitem{}{Wine tasting}{}{Cooking}
\cvdoubleitem{}{Skiing}{}{Ping Pong}
\cvdoubleitem{}{Yoga}{}{Pool}

\end{document}

%% end of file `Resume_Baris_Aydinoglu.tex'.
